\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}

### 2019-07-26 article/article.tex
Working on the Related Work section

\section{Related Work}
%#Yet to be researched

>>>>

\section{Related Work}
Some similar work has been done using both graph databases and their references. This work is listed here.
\item \textbf{Cross Ref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications. BibTrek stores publications as nodes in the database and relates every available node through their references. While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user inputed publications that have been dynamically fetched from different libraries. 
\item \textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} is an application that using several books' BibTeX metadata and a Neo4J graph representation, through the use of user inputed cypher queries, about either the author's name or book type, reccommends us a book. Similarly to BibTrek a Neo4J graph representation is used after parsing a book's metadata. The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books. Finally, similarly to this application, BibTrek's Cypher queries are done to fetch the most referenced paper given a single author, keyword or publication title, making the scope different.
\item \textbf{VIS - Google Scholar Citation Visualisation} is an application that is used to create a graph based on a geographic map that has information about a publication, like for example, where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map. While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information. Finally BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far. %Nao tenho a certeza deste ultimo paragrafo no entanto. O VIS se calhar tambem faz isto.
